### 2022-09-30 main/chapter_theory.tex
less neutrino mass: use an atlas measurement

When `nobody knows' the answer to a riddle, the status lies somewhere between
two extremes:
either many answers are satisfactory with no clear best,
or no satisfactory answers are yet known.
We distinguish these two cases with the labels
\emph{uncertain} and \emph{unknown} respectively:
the model of neutrino masses is mostly \emph{uncertain}, but
the reconciliation of quantum field theory with general relativity is
mostly \emph{unknown}.

>>>>

When `nobody knows' the answer to a riddle, the status lies somewhere between
two extremes:
either many answers are satisfactory with no clear best,
or no satisfactory answers are yet known.
We distinguish these two cases with the labels
\emph{uncertain} and \emph{unknown} respectively:
the top quark mass is slightly \emph{uncertain}, but
the reconciliation of quantum field theory with general relativity is
mostly \emph{unknown}.
